%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Senior Research and Development Engineer} % Job title
{Li Auto Inc.} % Organization
{Shanghai} % Location
{Jan. 2024 - now} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {1. deliver 3D vehicle assets (3DRC dataset)}
\item {2. deploy multi-agent dynamics in closed-loop simulation + simulator optimization}
\item {3. feedforward simulator}
\end{cvitems}
}

\cventry
{Staff Research Engineer} % Job title
{Huawei 2012 Labs} % Organization
{Shenzhen} % Location
{Jan. 2023 - Dec. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Urban region reconstruction with drones}
\end{cvitems}
}

\cventry
{Research Intern} % Job title
{Synthesia} % Organization
{London, UK} % Location
{Jun. 2022 - Oct. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {High-fidelity Neural Actor}
\end{cvitems}
}

\cventry
{Research Intern} % Job title
{Facebook} % Organization
{Seattle, USA} % Location
{Jun. 2021 - Oct. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Semantic 3D reconstruction for eye tracking}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Google} % Organization
{Remote} % Location
{Apr. 2015 - Sep. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developing \href{https://github.com/tiny-dnn/tiny-dnn}{\color{awesome-skyblue}{\underline{tiny-dnn}}}, \textit{e.g.} a deep learning backend;
3 submodules: \href{https://www.youtube.com/watch?v=Mc20rTYdXTE}{\color{awesome-skyblue}{\underline{3D metric learning}}}, \href{https://summerofcode.withgoogle.com/archive/2016/projects/4623962327744512}{\color{awesome-skyblue}{\underline{quantized deep learning}}} and \href{https://summerofcode.withgoogle.com/archive/2019/projects/6247164785721344}{\color{awesome-skyblue}\underline{super resolution}}.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
